### 2008-09-15 trunk/Latex/H2Preview/H2PrevFI.tex
First set of changes: major changes to simple example conclusions. Also mods to feedforward...

\begin{rem}
\label{rem:FIminwandr}
The full-information controller which minimises $\nrm{T_{v\rightarrow z}}_2$ also minimises $\nrm{T_{\eta\rightarrow z}}_2$ and $\nrm{T_{w\rightarrow z}}_2$. This type of relationship is true for any partition of the exogenous disturbance signal in an $\htwo$ full-information generalised regulator problem, and it is not a particular feature of the preview control problem. To see this, note that the two minimisation problems:
\begin{eqnarray}
\min_{K_{FI}}\nrm{T_{\eta\rightarrow z}}_2 \label{norm1} \\
\min_{K_{FI}}\nrm{T_{w\rightarrow z}}_2, \label{norm2}
\end{eqnarray}
are related by the choice of $B_1$ and $D_{11}$, and that computation of the controller gain $F_{2}$ is independent of these matrices. The feedforward control gains $F_{0r}$ and $F_{0w}$ can be chosen independently, and so it is possible to simultaneously minimise $\nrm{T_{\eta\rightarrow z}}_2$ and $\nrm{T_{w\rightarrow z}}_2$. Since $\nrm{T_{v \rightarrow z}}_2 = \nrm{T_{\eta\rightarrow z}}_2 + \nrm{T_{w \rightarrow z}}_2$, a controller satisfying (\ref{norm1}) and (\ref{norm2}) also minimizes $\nrm{T_{v \rightarrow z}}_2$.
\end{rem}

>>>>

\begin{rem}
\label{rem:FIminwandr}
The full-information controller which minimises $\nrm{T_{v\rightarrow z}}_2$ also minimises $\nrm{T_{\eta\rightarrow z}}_2$ and $\nrm{T_{w\rightarrow z}}_2$. This type of relationship is true for any partition of the exogenous disturbance signal in an $\htwo$ full-information generalised regulator problem, and it is not a particular feature of the preview control problem. To see this, note that the two minimisation problems:
\begin{eqnarray}
\min_{K_{FI}}\nrm{T_{\eta\rightarrow z}}_2 \label{norm1} \\
\min_{K_{FI}}\nrm{T_{w\rightarrow z}}_2, \label{norm2}
\end{eqnarray}
are related by the choice of $B_1$ and $D_{11}$, and that computation of the controller gain $F_{2}$ is independent of these matrices. The feedforward control gains $F_{0r}$ and $F_{0w}$ can be chosen independently, and so it is possible to simultaneously minimise $\nrm{T_{\eta\rightarrow z}}_2$ and $\nrm{T_{w\rightarrow z}}_2$. Since $\nrm{T_{v \rightarrow z}}^2_2 = \nrm{T_{\eta\rightarrow z}}^2_2 + \nrm{T_{w \rightarrow z}}^2_2$, a controller satisfying (\ref{norm1}) and (\ref{norm2}) also minimizes $\nrm{T_{v \rightarrow z}}_2$.
\end{rem}
